Analyzing State-Level Respondent Estimates Using Ratio Estimators: A Case Study with 2022 ACS Data

### 2024-11-22 paper/paper.qmd
Data Cleaning
Remove unused columns
Round numbers in table to one decimal place

We gather the data from IPUMS USA site, firstly we select “IPUMS USA” on the IPUMS, then clicked “Get Data”, then click “SELECT SAMPLE” and only select “2022 ACS”.  We choose state level data by selecting “HOUSEHOLD”, then choose “GEOGRAPHIC” and add “STATEICP” to cart. For individual level data, we directly search "EDUC" and add it to the cart. After that, we clicked “VIEW CART” , then  click  “CREATE DATA EXTRACT".  We modify the it to csv form. We clicked “SUBMIT EXTRACT" and download it.

@@

data <- read.csv(file = here::here("data/01-raw_data/usa_00001.csv"))

@@

# Apply the ratio to estimate total number of respondents in each state
estimated_data <- doctoral_data %>%
  mutate(estimated_total_respondents = doctoral_count / california_ratio)

>>>>

We gather the data from IPUMS USA site, firstly we select “IPUMS USA” on the IPUMS, then clicked “Get Data”, then click “SELECT SAMPLE” and only select “2022 ACS”.  We choose state level data by selecting “HOUSEHOLD”, then choose “GEOGRAPHIC” and add “STATEICP” to cart. For individual level data, we directly search "EDUC" and add it to the cart. After that, we clicked “VIEW CART” , then  click  “CREATE DATA EXTRACT".  We modify the it to csv form. We clicked “SUBMIT EXTRACT" and download it. The data will not be uploaded to github due to its large size, and the prohibition of IPUMs.

@@

data <- read.csv(file = here::here("data/02-analysis_data/analysis_data.csv"))

@@

# Apply the ratio to estimate total number of respondents in each state
estimated_data <- doctoral_data %>%
  mutate(estimated_total_respondents = round(doctoral_count / california_ratio, 1))
